Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-17 GWLDCII.tex
one more sentence
fiddled with R(W)/R(e) text

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}, Theorem~\ref{res alg gives correct GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. Furthermore, the above algorithm allows us to better understand the positroids associated to Wilson loop. In particular, Corollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops. Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} and Theorem~\ref{res alg gives correct GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$. In fact, it can be read directly off of $C(W)$ in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}). In Algorithm~\ref{alg WLD to denom via GN} we give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

>>>>

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}, Theorem~\ref{res alg gives correct GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. This makes it much easier to track how properties move through the bijection, as we do throughout the later sections. Furthermore, the above algorithm allows us to better understand the positroids associated to Wilson loop. In particular, Corollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops. Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} and Theorem~\ref{res alg gives correct GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

This formulation for the denominator comes from the physics literature: see equation (2) in \cite{HeslopStewart}. In Section \ref{sec poles}, we give a geometric meaning to the factors, $\{R_e | e \in V\}$, of $R(W)$.  Given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ ((see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassman necklace. In particular, \emph{which} minors of $C(W)$ contribut to $R(W)$ is geometrically determined. Furthermore, when two Wilson loop diagrams correspond to the same postroid cell, they still have different $R(W)$. In Algorithm~\ref{alg WLD to denom via GN} we give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
